Supervised Reinforcement Learning with Partial States: \\ a Teaching Method for Action Selection for HRI

### 2017-07-21 paper.tex
Pass on example and future work

In the current implementation, the state is defined by the distance between each
animals and their life. With these features selected, the partial state
transmitted to the user is the distance between the eagle, the eagle's life and
the rat's life. Similarly, when selected an action, the supervisor can also
select features in the state relevant to the selction.

Limitations of the approach reside in the difference of
representation of the state and action spaces between the supervisor and the
algorithm and limits in the communication. For example a user could try to move
an animal close to another one,
and depending of the represenation of the actions on the algorithm side, the
action might not be understood in the same way. Similarly, features used by the
supervisor to select actions might not be represented in the state used by the
algorithm. And lastly, in the case of implicit selection of features, a single
case of features representatin (for example highlighting two animals) might not
be perceived in the same way by observers.

>>>>

In the current implementation, the state is defined by the distance between each
animals and their life. With these features selected, the partial state
transmitted to the user is the distance between the eagle and the rat, the eagle's life and
the rat's life. Similarly, when selecting an action, the supervisor can 
select features in the state relevant to the selection.

The main limitations of the approach reside in the difference of
representation of the state and action spaces between the supervisor and the
algorithm and the limit in communication. For example a user could try to move
an animal close to another one,
and depending of the represenation of the actions on the algorithm side, the
action might not be understood in the same way. Similarly, features used by the
supervisor to select actions might not be represented in the state used by the
algorithm. And lastly, in the case of implicit selection of features, a single
case of features representatiion (for example highlighting two animals) might not
be perceived in the same way by observers.
